### 2022-02-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@ac3aadc9dd93816520066c49d8cb7bcecbb6ad8a 🚀

Here, we present a general method to infer potential trophic
interactions, relying on the transfer learning of network
representations, specifically by using similarities of species in a
biologically/ecologically relevant proxy space (\emph{e.g.} shared
morphology or ancestry). Transfer learning is a machine learning
methodology that uses the knowledge gained from solving one problem and
applying it to a related (destination) problem (Pan \& Yang, 2010;
Torrey \& Shavlik, 2010). In this instance, we solve the problem of
predicting trophic interactions between species, based on knowledge
extracted from another species pool for which interactions are known by
using phylogenetic structure as a medium for transfer. There is a
plurality of measures of species similarities that can be used for
inferring \emph{potential} species interactions \emph{i.e.} metaweb
reconstruction (see \emph{e.g.} Morales-Castilla et al., 2015); however,
phylogenetic proximity has several desirable properties when working at
large scales. Gerhold et al. (2015) made the point that phylogenetic
signal captures diversification of characters (large macro-evolutionary
process), but not necessarily community assembly (fine ecological
process); Dormann et al. (2010) previously found very similar
conclusions. Interactions tend to reflect a phylogenetic signal because
they have a conserved pattern of evolutionary convergence that
encompasses a wide range of ecological and evolutionary mechanisms
(Cavender-Bares et al., 2009; Mouquet et al., 2012), and - most
importantly - retain this signal even if it is obscured at the community
scale due to \emph{e.g.} local conditions (Hutchinson et al., 2017;
Poisot \& Stouffer, 2018). Finally, species interactions at
macro-ecological scales seem to respond mostly to macro-evolutionary
processes (Price, 2003); which is evidenced by the presence of conserved
backbones in food webs (Dalla Riva \& Stouffer, 2016; Mora et al.,
2018), strong evolutionary signature on prey choice (Stouffer et al.,
2012), and strong phylogenetic signature in food web intervality (Eklöf
\& Stouffer, 2016). Phylogenetic reconstruction has also previously been
used within the context of ecological networks, namely understanding
ancestral plant-insect interactions (Braga et al., 2021). Taken
together, these considerations suggest that phylogenies can reliably be
used to transfer knowledge on species interactions.

@@

@@

\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
Thuiller, W. (2020a). TETRA-EU 1.0: A species-level trophic metaweb of
European tetrapods. \emph{Global Ecology and Biogeography},
\emph{29}(9), 1452--1457. \url{https://doi.org/10.1111/geb.13138}

@@

\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
Mora, B. B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer, D.
B. (2018). Identifying a common backbone of interactions underlying food
webs from different ecosystems. \emph{Nature Communications},
\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}

>>>>

Here, we present a general method to infer potential trophic
interactions, relying on the transfer learning of network
representations, specifically by using similarities of species in a
biologically/ecologically relevant proxy space (\emph{e.g.} shared
morphology or ancestry). Transfer learning is a machine learning
methodology that uses the knowledge gained from solving one problem and
applying it to a related (destination) problem (Pan \& Yang, 2010;
Torrey \& Shavlik, 2010). In this instance, we solve the problem of
predicting trophic interactions between species, based on knowledge
extracted from another species pool for which interactions are known by
using phylogenetic structure as a medium for transfer. There is a
plurality of measures of species similarities that can be used for
inferring \emph{potential} species interactions \emph{i.e.} metaweb
reconstruction (see \emph{e.g.} Morales-Castilla et al., 2015); however,
phylogenetic proximity has several desirable properties when working at
large scales. Gerhold et al. (2015) made the point that phylogenetic
signal captures diversification of characters (large macro-evolutionary
process), but not necessarily community assembly (fine ecological
process); Dormann et al. (2010) previously found very similar
conclusions. Interactions tend to reflect a phylogenetic signal because
they have a conserved pattern of evolutionary convergence that
encompasses a wide range of ecological and evolutionary mechanisms
(Cavender-Bares et al., 2009; Mouquet et al., 2012), and - most
importantly - retain this signal even if it is obscured at the community
scale due to \emph{e.g.} local conditions (Hutchinson et al., 2017;
Poisot \& Stouffer, 2018). Finally, species interactions at
macro-ecological scales seem to respond mostly to macro-evolutionary
processes (Price, 2003); which is evidenced by the presence of conserved
backbones in food webs (Bramon Mora et al., 2018; Dalla Riva \&
Stouffer, 2016), strong evolutionary signature on prey choice (Stouffer
et al., 2012), and strong phylogenetic signature in food web intervality
(Eklöf \& Stouffer, 2016). Phylogenetic reconstruction has also
previously been used within the context of ecological networks, namely
understanding ancestral plant-insect interactions (Braga et al., 2021).
Taken together, these considerations suggest that phylogenies can
reliably be used to transfer knowledge on species interactions.

@@

\leavevmode\hypertarget{ref-BramonMora2018IdeCom}{}%
Bramon Mora, B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer,
D. B. (2018). Identifying a common backbone of interactions underlying
food webs from different ecosystems. \emph{Nature Communications},
\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}

@@

\leavevmode\hypertarget{ref-Maiorano2020TetSpe}{}%
Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
Thuiller, W. (2020a). TETRA-EU 1.0: A species-level trophic metaweb of
European tetrapods. \emph{Global Ecology and Biogeography},
\emph{29}(9), 1452--1457. \url{https://doi.org/10.1111/geb.13138}

@@
